A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers

### 2019-03-01 Thesis/Intro/Introduction.tex
Updated introduction

\section{Tuneable Lasers}
\begin{figure}[htbp]
\centering
\input{./Figures/Cavity}
\caption[Laser Cavity]{Laser cavity schematic.}
\label{fig:cavity}
\end{figure}

@@

FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, becker, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}. Both methods cause the periodic nature of the refractive index through interference. In the phase-mask method (Figure \ref{fig:phasemask}) a single beam of UV light passes through the phase-mask which acts as a series of lenses, focusing the light at the core---this causes a sinusoidal interference pattern. Similarly, in the holographic side exposure method (Figure \ref{fig:holographic}), two beams of UV light are instead used to create the interference pattern. \\

@@

Spontaneous emission is the process in which an electron of an atom that is in an excited state emits a photon as it transitions to a lower energy state. The energy of the photon is equal to the energy difference between the two levels. On the other hand, in stimulated emission an incident photon triggers this emission \cite{alazzawi}. The rare-earth metal ions are excited by the pump laser, and when they interact with a photon of the tuneable laser, a new photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}. \\

>>>>

\section{Tuneable Lasers}
\begin{figure}[tbp]
\centering
\input{./Figures/Cavity}
\caption[Laser Cavity]{Laser cavity schematic.}
\label{fig:cavity}
\end{figure}

@@

FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002,alazzawi,becker,starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}. Both methods cause the periodic nature of the refractive index through interference. In the phase-mask method (Figure \ref{fig:phasemask}) a single beam of UV light passes through the phase-mask which acts as a series of lenses, focusing the light at the core---this causes a sinusoidal interference pattern. Similarly, in the holographic side exposure method (Figure \ref{fig:holographic}), two beams of UV light are instead used to create the interference pattern. \\

@@

\begin{figure}[tbp]
\centering
\input{./Figures/Emission}
\caption{In pumping, incident photons are absorbed by electrons which are then excited into a higher energy state. In spontaneous emission, an electron in an excited state emits a photon and returns to the lower energy state. Finally, in stimulated emission, an incident photon interacts with an electron in an excited state, the electron donates its energy to the photon and returns to the lower energy state.}
\label{fig:emission}
\end{figure}

Spontaneous emission is the process in which an electron of an atom that is in an excited state emits a photon as it transitions to a lower energy state. The energy of the photon is equal to the energy difference between the two levels. On the other hand, in stimulated emission an incident photon triggers this emission \cite{alazzawi}. The rare-earth metal ions are excited by the pump laser, and when they interact with a photon of the tuneable laser, a new photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}. These processes are highlighted in Figure \ref{fig:emission}. \\
